\plaintitle

### 2016-09-21 drafts/labor/complexity.tex
remove flexibility. no flexibility!

\documentclass[trackingWork]{subfiles}
\onlyinsubfile{
  \usepackage{xr-hyper}
  \usepackage{hyperref}
}

@@

\subsubsubsection{\pieceworkpers}
\topic{Piecework researchers have found themselves trying to understand what characteristics limit piecework,
or more precisely what has prevented piecework from becoming more prevalent.}
The research into piecework makes the case that
piecework has been limited principally by the challenges of human management and oversight.
\citeauthor{10.2307/23702539} describes a case study in Santa Fe Railway, which
deployed scientific management and a piecework regime in an attempt to stymie rising repair costs
\cite{10.2307/23702539}.
\citeauthor{10.2307/23702539} reports on the hiring of Harrington Emerson,
an ``efficiency expert'', who went on to develop a ``standard time'' for each task at the company
informed by ``thousands of individual operations at the Topeka shops''.
The cost of measuring workers in such excruciating detail at the turn of the \nth{20} century was undoubtedly immense,
but this ``standard time'' value, which determined the pay that workers would earn for each task they do,
was the only viable approach at the time to determine appropriate pay given the task
\cite{10.2307/23702539}.
But the repeated measurement of workers' time to complete tasks had shortcomings;
for one thing, pay rates for rarer tasks
were necessarily less certain than for more common tasks,
which had the simple benefit of a larger sample size.
\ali{Do I need ``for another thing\dots''? This paragraph is kind of huge already. Not sure how to break it up/down as it is.}
One might conclude from \citeauthor{10.2307/23702539}'s observations that
complex, creative work --- which is inherently heterogeneous and difficult to routinize ---
would be unsuitable for piecework.
% We might reflect on \citeauthor{hart2016rise}'s piecework's limitations,
% and specifically the challenge of multidimensional work
% --- tasks comprising of numerous, sometimes conflicting, goals
% \cite{hart2016rise}.

% It would be reasonable, then, to infer that work like this
% --- reasonably highly skilled work where quality is difficult to assess ---
% would be unsuitable for piecework.
% \msb{that conclusion came way too fast. give a little detail on the railway. how did they come to that conclusion?}

% \msb{this paragraph needs a topic sentence. it's a wandering paragraph currently. is the claim here that evaluation is the limiting factor?}
\topic{Determining appropriate pay rates, informed by the careful measurement of workers,
isn't the only major challenge piecework faced; evaluation proved a limiting factor as well.}
\citeauthor{10.2307/23702539} enumerates some of the roles required
to facilitate piecework in the early \nth{20} century --- among them
    ``\dots~piecework clerks, inspectors, and `experts'\dots''
\cite{10.2307/23702539}.
% \citeauthor{10.2307/23702539} and \citeauthor{hart2016rise} may seem
% to be making differing claims about the limitations of piecework, but
% we argue that \citeauthor{10.2307/23702539}
% is simply making a more concrete observation illustrating the insight that
% \citeauthor{hart2016rise} later makes.
\citeauthor{10.2307/23702539} further recognizes that
it's necessary for a successful piecework shop to employ
clerks,
inspectors, and
other experts to properly design and evaluate complex work.
\citeauthor{hart2016rise} later makes a more concrete observation of this hurdle,
as he argues an ultimate limit to how far this can go;
at some point, evaluating multidimensional work output for quality
(rather than for quantity) becomes infeasible.
In his words,
``if the quality of the output is more difficult to measure than the quantity,
perhaps because of `difficult--to--observe' production techniques,
then a piecework system is likely to encourage
an over--emphasis on quantity produced and an under-emphasis on quality''
\cite{hart2016rise}.
This, \citeauthor{hart2016rise} argues, may have fundamentally hamstrung piecework,
and ultimately precipitated its downfall,
especially with the increasing complexity of manufacturing work
over the course of the \nth{20} century.
\ali{just to be clear, this whole point is queuing up so that later I can be like
``Oh hey computers are terrific at evaluating some stuff really quickly.
And researchers in crowd work have done some work on workers evaluating other workers
(e.g. Find--Fix--Verify, arguably \textit{PeerStudio} does something along this line)
\cite{bernsteinSoylent,Kulkarni:2015:PRP:2724660.2724670}''}

\topic{The research seems to suggest that it was difficult to apply piecework to more skilled work,
particularly because maximizing on the advantages of piecework seemed to reward
smaller, more constrained, more narrowly trained tasks.}
For most of the \nth{19} century,
piecework was applied almost exclusively to farm and textile work.
% \citeauthor{grier2013computers} describes Airy's training and employment of young men to compute astronomical observations,
% mentioning that boys needed only to have ``the basic skills of mathematics''
% \cite{grier2013computers}.
% \citeauthor{hart2013rise} argue that piecework flourished in the first half of the \nth{20} century because
% tasks were decomposed --- a discussion we will return to later ---
% such that untrained workers could be trained relatively quickly on a very narrowly designed task
% \cite{hart2013rise}.
Work was simple and widely understood
--- farm workers didn't need to be trained on how to plow fields, or birth foals;
seamstresses knew how to sew together denim
\cite{10.2307/2338394,riisOtherSideLives}.
% The general argument for decomposition, we will see later,
% hinges on the promise that
% tasks can be \textit{made} less complex and time--consuming,
% if they're not already so.
% \ali{this section is here because i later talk about the complexity of work, and
% I want to keep the whole thing about how Uber, Google Maps, etc\dots make it possible to
% \begin{inlinelist}
% \item train workers more quickly (honestly just transmitting instructions over the Internet is so much quicker than what Airy had), and
% \item give workers necessary tools/information to get work done
% (e.g. ``Waze knows you should avoid the intersection 3 blocks down the road because of an accident''
% and (maybe) ``not great at math? WolframAlpha can confirm or just give you your answer'')
% \end{inlinelist}.}

\topic{This isn't to say that complex work is outside of the realm of piecework;
indeed, we've discussed complex applications of crowd work already.}
% As \citeauthor{hart2013rise} described,
While \citeauthor{hart2013rise} described a flourishing of ingenious piecework design,
much of it arose out of necessity ---
% almost strictly out of necessity ---
it was infeasible to provide new workers with
the comprehensive education that was familiar to men through apprenticeships
\cite{hart2013rise}.
While this constraint led to much more tightly scoped work
% (perhaps surprisingly at the time) more efficient allocations of workers,
who now had to specialize in extremely narrowly defined roles.
The same could be said of Airy and his \textit{computers}
--- young boys whose preparations consisted principally of
a relatively specific mathematics curriculum
\cite{grier2013computers}.
Instead, we argue that the literature suggests that
piecework is tightly limited only when the application of piecework follows
a direct, perhaps even unimaginative,
mapping from an time--based regime to an output--based one.
When the work is redesigned from the ground up 
--- as we see with mathematicians in the \nth{19} century and
with the metalworking industry during the Second World War ---
it seems that we don't yet know the limits of complexity with regard to piecework.
% \msb{so what are we to take out of this? that there is no limit? just our creativity?}
\ali{This is \textit{almost} making a prediction,
but I wanted to take something punchy away from the stuff I cite here.}

>>>>

\documentclass[trackingWork]{subfiles}

@@

\subsubsubsection{\pieceworkpers}
\topic{Piecework researchers have found themselves trying to understand what characteristics limit piecework,
or more precisely what has prevented piecework from becoming more prevalent.}
The research into piecework makes the case that
piecework has been limited principally by the challenges of human management and oversight.
\citeauthor{10.2307/23702539} describes a case study in Santa Fe Railway, which
deployed scientific management and a piecework regime in an attempt to stymie rising repair costs
\cite{10.2307/23702539}.
\citeauthor{10.2307/23702539} reports on the hiring of Harrington Emerson,
an ``efficiency expert'', who went on to develop a ``standard time'' for each task at the company
informed by ``thousands of individual operations at the Topeka shops''.
The cost of measuring workers in such excruciating detail at the turn of the \nth{20} century was undoubtedly immense,
but this ``standard time'' value, which determined the pay that workers would earn for each task they do,
was the only viable approach at the time to determine appropriate pay given the task
\cite{10.2307/23702539}.
But the repeated measurement of workers' time to complete tasks had shortcomings;
for one thing, pay rates for rarer tasks
were necessarily less certain than for more common tasks,
which had the simple benefit of a larger sample size.
\ali{Do I need ``for another thing\dots''? This paragraph is kind of huge already. Not sure how to break it up/down as it is.}
One might conclude from \citeauthor{10.2307/23702539}'s observations that
complex, creative work --- which is inherently heterogeneous and difficult to routinize ---
would be unsuitable for piecework.

\topic{Determining appropriate pay rates, informed by the careful measurement of workers,
isn't the only major challenge piecework faced; evaluation proved a limiting factor as well.}
\citeauthor{10.2307/23702539} enumerates some of the roles required
to facilitate piecework in the early \nth{20} century --- among them
    ``\dots~piecework clerks, inspectors, and `experts'\dots''
\cite{10.2307/23702539}.
\citeauthor{10.2307/23702539} further recognizes that
it's necessary for a successful piecework shop to employ
clerks,
inspectors, and
other experts to properly design and evaluate complex work.
\citeauthor{hart2016rise} later makes a more concrete observation of this hurdle,
as he argues an ultimate limit to how far this can go;
at some point, evaluating multidimensional work output for quality
(rather than for quantity) becomes infeasible.
In his words,
``if the quality of the output is more difficult to measure than the quantity,
perhaps because of `difficult--to--observe' production techniques,
then a piecework system is likely to encourage
an over--emphasis on quantity produced and an under-emphasis on quality''
\cite{hart2016rise}.
This, \citeauthor{hart2016rise} argues, may have fundamentally hamstrung piecework,
and ultimately precipitated its downfall,
especially with the increasing complexity of manufacturing work
over the course of the \nth{20} century.
\ali{just to be clear, this whole point is queuing up so that later I can be like
``Oh hey computers are terrific at evaluating some stuff really quickly.
And researchers in crowd work have done some work on workers evaluating other workers
(e.g. Find--Fix--Verify, arguably \textit{PeerStudio} does something along this line)
\cite{bernsteinSoylent,Kulkarni:2015:PRP:2724660.2724670}''}

\topic{The research seems to suggest that it was difficult to apply piecework to more skilled work,
particularly because maximizing on the advantages of piecework seemed to reward
smaller, more constrained, more narrowly trained tasks.}
For most of the \nth{19} century,
piecework was applied almost exclusively to farm and textile work.
Work was simple and widely understood
--- farm workers didn't need to be trained on how to plow fields, or birth foals;
seamstresses knew how to sew together denim
\cite{10.2307/2338394,riisOtherSideLives}.

\topic{This isn't to say that complex work is outside of the realm of piecework;
indeed, we've discussed complex applications of crowd work already.}
While \citeauthor{hart2013rise} described a flourishing of ingenious piecework design,
much of it arose out of necessity ---
it was infeasible to provide new workers with
the comprehensive education that was familiar to men through apprenticeships
\cite{hart2013rise}.
While this constraint led to much more tightly scoped work
who now had to specialize in extremely narrowly defined roles.
The same could be said of Airy and his \textit{computers}
--- young boys whose preparations consisted principally of
a relatively specific mathematics curriculum
\cite{grier2013computers}.
Instead, we argue that the literature suggests that
piecework is tightly limited only when the application of piecework follows
a direct, perhaps even unimaginative,
mapping from an time--based regime to an output--based one.
When the work is redesigned from the ground up 
--- as we see with mathematicians in the \nth{19} century and
with the metalworking industry during the Second World War ---
it seems that we don't yet know the limits of complexity with regard to piecework.
\ali{This is \textit{almost} making a prediction,
but I wanted to take something punchy away from the stuff I cite here.}

### 2016-09-21 drafts/labor/decomposition.tex
expanding on relationships
abstract and title closed out
intro notes resolved, some requests for feedback i also changed it so that \ali and \msb notes don't show up in the final document, but do show up in the constituent parts. if you want to undo that, comment lines 124-127 (or just 126-127)
remove flexibility. no flexibility!

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}

\subsubsection[the decomposition of work]{The Decomposition of Work}\label{sec:decomposition}

\subsubsubsection{\crowdworkpers}
\topic{The crowdsourcing research into work decomposition
has largely focused on minimizing the additional context necessary to do tasks%
, and making it easier to do tasks with less time.}
This first thread is
perhaps best described by \citeauthor{verroios2014context} as
making crowd workers ``\dots able to act with
global understanding when each contributor only has access to local views''
\cite{verroios2014context}.
With the exception of a few cases
(specifically, \citeauthor{Kinnaird:2012:WTM:2389176.2389219}'s work
which finds that greater work context fosters more reliably high--quality work)%
, the micro task paradigm has emerged as the overwhelming favorite
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016%
,       cheng2015break,Kinnaird:2012:WTM:2389176.2389219}.

\topic{As the additional context necessary to complete a task diminishes%
, the marginal cost of finding and
\textit{doing} tasks has increasingly become the focus of research.}
\citeauthor{taskSearch} illustrate the challenges on AMT%
, and some work has gone into ameliorating the problems specific to this work site
(\textit{ReLauncher}), % does anyone care for project names?
while other work designs tasks around gap time
(\textit{Twitch Crowdsourcing} \& \textit{Wait--Learning})
\cite{taskSearch,KucherbaevReLauncher,Vaish:2014:TCC:2611222.2556996%
,       Cai:2015:WLW:2702123.2702267}.
% \topic{One of the emergent properties of micro--tasks has been the relative cost of
%     \textit{finding} worthwhile tasks.}
%     The research community has documented and to some extent attempted to intervene in
%     the discovery of worthwhile tasks
%     \cite{taskSearch}.
\citeauthor{Cosley:2007:SUI:1216295.1216309}
attempts to address this by
directing workers to tasks through
``intelligent task routing''
\cite{Cosley:2007:SUI:1216295.1216309}.
Much of this work and the work at the periphery of this space, then%
, has focused on
minimizing the amount of time that people need to spend doing
anything other than the work for which they are paid.

Earlier we discussed \citeauthor{cheng2015break}'s work
measuring the impact that interruption has on worker performance
\cite{cheng2015break}.
This work illustrates a broader sentiment in
both the study and practice
of crowd work, that microtasks should be designed resiliently against the variability of workers%
, fully exploiting the abstracted nature of each piece of work
\cite{interruptionIqbal,delayAndOrderLasecki,vaish2014low}.
That is to say, micro--tasks should be designed such that a single worker's poor performance%
, or a good worker's sudden departure%
, does not significantly impact the agenda of the work as a whole.
While \citeauthor{cheng2015break} found costs with breaking tasks into smaller components
in the form of higher cumulative time to complete
(albeit much shorter real time to complete, owing to parallelization)%
, \citeauthor{delayAndOrderLasecki} found that at least \textit{some} performance can be recouped by stringing 
similar tasks together
\cite[respectively]{cheng2015break,delayAndOrderLasecki}.

Yet more work looks at the general framing of tasks%
, chaining and arranging them to maximally exploit
the attention and stress threshold % ???
of workers
\cite{Cai:2016:CRI:2858036.2858237}.
Rather than attempt to minimize the error rates in micro--tasks%
, as \citeauthor{Kinnaird:2012:WTM:2389176.2389219} suggested%
, we as a community have leaned \textit{into} the peril of
low--context work%
, ``embracing error'' in crowdsourcing
\cite{embracingErrorKrishna}.

\subsubsubsection{\pieceworkpers}
\topic{The research community relating to
piecework and labor
has been wrestling with the decomposition of work for centuries.}
The beginnings of
systematic task decomposition
stretch back as far as the \nth{17} century%
, when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics, including
`Arithmetic, the use of Logarithms, and Elementary Algebra'~''
to compute, by hand, astronomical phenomena
\cite{grier2013computers}.
These workers became the first \textit{computers}.

The work Airy solicited was interesting for several reasons.
First, work output was quickly verifiable;
Airy could assign variably skilled workers to compute values%
, and have other workers check their work.
Second, tasks were discrete --- that is, independent from one another.
Finally, knowledge of the full scope of the project
--- indeed, knowledge of anything more than the problem set at hand ---
was unnecessary.

The insight of breaking tasks down into smaller components didn't find its audience until
the early \nth{20} century%
, with the rise of Fordism and scientific management (or Taylorism).
From scientific management, we found that
we could measure work at unprecedented resolution and precision.
As \citeauthor{Brown01041990} points out%
, piecework most greatly benefits the instrumented measurement of workers, but certainly
in Ford and Taylor's time --- and certainly in Airy's time ---
highly instrumented, automatic measurement of workers was all but impossible.
As a result%
, the distillation of work into smaller chunks
ultimately reached a limit of usefulness.

>>>>

\documentclass[trackingWork]{subfiles}
% \makeatletter
% \def\blx@maxline{77}
% \makeatother
\onlyinsubfile{\usepackage{xr-hyper}
\usepackage{hyperref}
\externaldocument{complexity}
\externaldocument{relationships}
\externaldocument{decomposition}
}
\begin{document}

\subsubsection[How far can work be decomposed into smaller and smaller microtasks]{Decomposing Work}\label{sec:decomposition}

\subsubsubsection{\crowdworkpers}
\topic{The crowdsourcing research into work decomposition
has largely focused on minimizing the additional context necessary to do tasks,
and making it easier to do tasks with less time.}
This first thread is
perhaps best described by \citeauthor{verroios2014context} as
making crowd workers ``\dots able to act with
global understanding when each contributor only has access to local views''
\cite{verroios2014context}.
With the exception of a few cases
(specifically, \citeauthor{Kinnaird:2012:WTM:2389176.2389219}'s work
which finds that greater work context fosters more reliably high--quality work),
the micro task paradigm has emerged as the overwhelming favorite
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016,
      cheng2015break,Kinnaird:2012:WTM:2389176.2389219}.

\topic{As the additional context necessary to complete a task diminishes,
the marginal cost of finding and
\textit{doing} tasks has increasingly become the focus of research.}
\citeauthor{taskSearch} illustrate the challenges on AMT,
and some work has gone into ameliorating the problems specific to this work site
(\textit{ReLauncher}), % does anyone care for project names?
while other work designs tasks around gap time
(\textit{Twitch Crowdsourcing} \& \textit{Wait--Learning})
\cite{taskSearch,KucherbaevReLauncher,Vaish:2014:TCC:2611222.2556996,
      Cai:2015:WLW:2702123.2702267}.
% \topic{One of the emergent properties of micro--tasks has been the relative cost of
%     \textit{finding} worthwhile tasks.}
%     The research community has documented and to some extent attempted to intervene in
%     the discovery of worthwhile tasks
%     \cite{taskSearch}.
\citeauthor{Cosley:2007:SUI:1216295.1216309}
attempts to address this by
directing workers to tasks through
``intelligent task routing''
\cite{Cosley:2007:SUI:1216295.1216309}.
Much of this work and the work at the periphery of this space, then,
has focused on
minimizing the amount of time that people need to spend doing
anything other than the work for which they are paid.

Earlier we discussed \citeauthor{cheng2015break}'s work
measuring the impact that interruption has on worker performance
\cite{cheng2015break}.
This work illustrates a broader sentiment in
both the study and practice
of crowd work, that microtasks should be designed resiliently against the variability of workers,
fully exploiting the abstracted nature of each piece of work
\cite{interruptionIqbal,delayAndOrderLasecki,vaish2014low}.
That is to say, micro--tasks should be designed such that a single worker's poor performance,
or a good worker's sudden departure,
does not significantly impact the agenda of the work as a whole.
While \citeauthor{cheng2015break} found costs with breaking tasks into smaller components
in the form of higher cumulative time to complete
(albeit much shorter real time to complete, owing to parallelization),
\citeauthor{delayAndOrderLasecki} found that at least \textit{some} performance can be recouped by stringing 
similar tasks together
\cite[respectively]{cheng2015break,delayAndOrderLasecki}.

Yet more work looks at the general framing of tasks,
chaining and arranging them to maximally exploit
the attention and stress threshold % ???
of workers
\cite{Cai:2016:CRI:2858036.2858237}.
Rather than attempt to minimize the error rates in micro--tasks,
as \citeauthor{Kinnaird:2012:WTM:2389176.2389219} suggested,
we as a community have leaned \textit{into} the peril of
low--context work,
``embracing error'' in crowdsourcing
\cite{embracingErrorKrishna}.

\subsubsubsection{\pieceworkpers}
\topic{The research community relating to
piecework and labor
has been wrestling with the decomposition of work for centuries.}
The beginnings of
systematic task decomposition
stretch back as far as the \nth{19} century,
when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics, including
`Arithmetic, the use of Logarithms, and Elementary Algebra'~''
to compute, by hand, astronomical phenomena
\cite{grier2013computers}.
These workers became the first \textit{computers}.

The work Airy solicited was interesting for several reasons.
First, work output was quickly verifiable;
Airy could assign variably skilled workers to compute values,
and have other workers check their work.
Second, tasks were discrete --- that is, independent from one another.
Finally, knowledge of the full scope of the project
--- indeed, knowledge of anything more than the problem set at hand ---
was unnecessary.

The insight of breaking tasks down into smaller components didn't find its audience until
the early \nth{20} century,
with the rise of Fordism and scientific management (or Taylorism).
From scientific management, we found that
we could measure work at unprecedented resolution and precision.
As \citeauthor{Brown01041990} points out,
piecework most greatly benefits the instrumented measurement of workers, but certainly
in Ford and Taylor's time --- and certainly in Airy's time ---
highly instrumented, automatic measurement of workers was all but impossible.
As a result,
the distillation of work into smaller chunks
ultimately reached a limit of usefulness.

\topic{Piecework researchers address a number of the problems with the decomposition of work,
and the conflicting pressures managers and workers put forth.}
\citeauthor{bewley1999wages} in particular points out that
the approach of paying workers by the piece is
``\dots~not practical for workers doing many tasks, because of
the cost of establishing the rates and because
piecework does not compensate workers for time spent switching tasks''.
Ultimately, \citeauthor{bewley1999wages} argues that
``[piecework is] infeasible, because \dots
total output is the joint product of varying groups of people''
\cite{bewley1999wages}.
\ali{This is becoming both
a complexity    argument and
a decomposition argument\dots
I'm okay with using \citeauthor{bewley1999wages} in both, but
I want people to read this paper and not be like
``wow this author sure got their money's worth from those three books!''}

### 2016-09-21 drafts/labor/relationships.tex
remove flexibility. no flexibility!

Early on, \citeauthor{turkopticon} highlighted
the information asymmetry between workers and requesters on AMT,
leading to the creation of \textit{Turkopticon}, a site which allows
Turkers to rate and review requesters
\cite{turkopticon}.
\citeauthor{dynamo} took this critique on information asymmetry and power imbalances a step further,
designing \textit{Dynamo} to facilitate
Turkers acting collectively to bring about changes to their circumstances
--- this led to the Academic Requester Guidelines
\cite{dynamo}.
This unbridled power that requesters have over workers and
the resultant stress and frustration that this generates
has been part of the undercurrent of research into
the tense relationships between workers and requesters
\cite{fixingChaos,dynamo}.

@@

\ali{What do I want to do/say here? I think I want to point to point out that
\dots~I dunno. I'll review the \citetitle{american1921problem} book and maybe some other stuff}

>>>>

Early on, \citeauthor{turkopticon} highlighted
the information asymmetry between workers and requesters on AMT,
leading to the creation of \TO, a site which allows
Turkers to rate and review requesters
\cite{turkopticon}.
\citeauthor{dynamo} took this critique on information asymmetry and power imbalances a step further,
designing \DO to facilitate
Turkers acting collectively to bring about changes to their circumstances
--- this led to the Academic Requester Guidelines
\cite{dynamo}.
This unbridled power that requesters have over workers and
the resultant stress and frustration that this generates
has been part of the undercurrent of research into
the tense relationships between workers and requesters
\cite{fixingChaos,dynamo}.

@@

The ethos of American labor advocacy organizations``not only as railroad employees but also as members of the larger life of the community''
and other notions of affiliation and recognition of shared underlying goals and hopes.
I could point to \citeauthor{riisOtherSideLives} and be like
``what \textit{he} did was illustrate through this relatively new medium --- photography ---
how bad pieceworkers had it, foreshadowing
this later urging by nascent labor advocacy groups to recognize that
workers all shared these problems and needed to associate.''

This can also foreshadow crowd sourcing efforts like
\TO~and \DO.
